### 2016-08-19 rebuttal.tex

\question In lines 567--568, ``performing symbolic quantum mechanics'' makes no sense. This should probably be ``computations'', ``solving problems related to'', etc.
\begin{solution}

\end{solution}

\question The sentence ``SymPy expressions are immutable trees of Python objects.'' doesn't belong in the conclusion. This can be moved to the appropriate place when discussing SymPy's architecture.
\begin{solution}
This sentence was removed.
\end{solution}

\question All ``submodules'' should be replaced by ``modules'' (examples:
lines 657, 662).
\label{rev1point37}
\begin{solution}
We are unclear how the reviewer is making distinctions between ``modules'',
``submodules'', and ``packages''. Our use coincides with the definitions used
in the official Python documentation (see
\url{https://docs.python.org/3/tutorial/modules.html#packages} and
\url{https://docs.python.org/3/glossary.html#term-package}). The distinction
between (sub)module and (sub)package in terms of Python libraries seems very
technical. To clarify things, we have modified the manuscript to use
``package'' only when referring to a library external to SymPy (such as
mpmath and Xy-pic).

### 2016-08-19 rebuttal.tex

\question The sentence ``SymPy expressions are immutable trees of Python objects.'' doesn't belong in the conclusion. This can be moved to the appropriate place when discussing SymPy's architecture.
\begin{solution}
This sentence was removed.
\end{solution}

\question All ``submodules'' should be replaced by ``modules'' (examples:
lines 657, 662).
\label{rev1point37}
\begin{solution}
We are unclear how the reviewer is making distinctions between ``modules'',
``submodules'', and ``packages''. Our use coincides with the definitions used
in the official Python documentation (see
\url{https://docs.python.org/3/tutorial/modules.html#packages} and
\url{https://docs.python.org/3/glossary.html#term-package}). The distinction
between (sub)module and (sub)package in terms of Python libraries seems very
technical. To clarify things, we have modified the manuscript to use
``package'' only when referring to a library external to SymPy (such as
mpmath and Xy-pic).

To avoid confusion, and to be consistent with the definitions used by the
official Python documentation, we have modified the manuscript to use
``submodule'' to refer to any module that is a dotted submodule of
\texttt{sympy}, such as \texttt{sympy.physics.quantum}. This is to emphasize
that these modules all live within the \texttt{sympy} namespace, as ``module''
can suggest a separate library.
\end{solution}

\question The sentences in lines 657--661 should swap places, because ``areas of mathematics'' are discrete mathematics, concrete mathematics, etc., while simplifying expressions, performing common calculus operations, pretty printing expressions, etc.\ belongs to common operations (``other areas'' is also fine, albeit slightly wrong).
\begin{solution}

### 2016-08-19 rebuttal.tex

\end{solution}

\question The sets support listing is unnaturally split in two by the ``This includes\ldots'' sentence which would fit better in parentheses.
\begin{solution}
This suggestion was implemented.
\end{solution}

\question Line 355, add a sentence explaining that in SymPy \texttt{str == repr}, because in Python \texttt{repr} is used to get an unambiguous valid Python code representation, while the return value of \texttt{str} is meant to be human-readable.
\begin{solution}
This footnote was added:
\begin{quote}
In SymPy, \texttt{str(expr) == repr(expr)}.  In other words,
string representation of an expression designed to be both compact,
human-readable and a valid Python code, that could be used to
recreate one.  As it was noted before, use \texttt{srepr} function to
see the exact form of an expression.
\end{quote}
\end{solution}

\question Lines 359 and 379: what is 2D text representation? It seems that ``2D'' shouldn't be here.
\begin{solution}
This sentence was replaced with:
\begin{quote}
Two-dimensional (2D) textual representation of the expression can
be printed with monospace fonts via \verb|pprint|.
\end{quote}
We use here the same terminology as in the Mathematica
online documentation, e.g., the
\href{https://reference.wolfram.com/language/ref/OutputForm.html}{\texttt{OutputForm}}
function:
\begin{quote}
\texttt{OutputForm[expr]}: prints as a two-dimensional representation of expr using only keyboard characters.
\end{quote}
\end{solution}

### 2016-08-19 printers.tex
Add an article
Clarify and cleanup str/repr footnote. Add a \ref to the srepr section.

SymPy has a rich collection of expression printers.
By default, an interactive Python session will render the
\verb|str| form of an expression, which has been used in all the examples in
this paper so far. The \verb|str| form of an expression is valid Python and
roughly matches what a user would type to enter the expression.

@@

Two-dimensional (2D) textual representation of the expression can
be printed with monospace fonts via \verb|pprint|.
Unicode characters are used for rendering mathematical symbols such as integral signs,
square roots, and parentheses. Greek letters and subscripts in symbol names
that have Unicode code points associated
are also rendered automatically.
% TODO cite unicode?

>>>>

SymPy has a rich collection of expression printers. By default, an interactive
Python session will render the \verb|str| form of an expression, which has
been used in all the examples in this paper so far. The \verb|str| form of an
expression is valid Python and roughly matches what a user would type to enter
the expression.\footnote{Many Python libraries distinguish the \texttt{str}
  form of an object, which is meant to be human-readable, and the
  \texttt{repr} form, which is mean to be valid Python that recreates the
  object. In SymPy, \texttt{str(expr) == repr(expr)}. In other words, the
  string representation of an expression is designed to be compact,
  human-readable, and valid Python code that could be used to recreate the
  expression. As it was noted in section~\ref{sec:core}, the \texttt{srepr}
  function prints the exact, verbose form of an expression.}

@@

A two-dimensional (2D) textual representation of the expression can
be printed with monospace fonts via \verb|pprint|.
Unicode characters are used for rendering mathematical symbols such as integral signs,
square roots, and parentheses. Greek letters and subscripts in symbol names
that have Unicode code points associated
are also rendered automatically.
% TODO cite unicode?
